---
title: "Data cleaning"
author: "Sara DeLaurentis"
date: "6/16/2022"
output:
  word_document:
    toc: yes
  html_document:
    toc: yes
    toc_float: yes
    theme: cerulean
    highlight: kate
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)
library(dplyr)
library(stringr)
library(glue)
library(knitr)
library(lubridate)


```

Purpose: Data cleaning - Compromised data and Outlier removal - create modified ALL.csv  
  
  
  
  
#### Data viewing and removal

```{r NA-collection, echo = TRUE}
data <- read.csv("ALL.csv")
#view(data)

#find NAs 
data.na <- data[is.na(data$value),]
na.length <- length(c(data.na$X))
na.namestring <- c(data.na$name[!duplicated(data.na$name)])


#is D2B_R3_lsurf_i90_2021 still in the file?
D2B_R3_lsurf <- data[grep("D2B_R3_lsurf_i90_2021", data$name),]
D2B_R3_l_length <- length(c(D2B_R3_lsurf$X))

```

2022-06-16: there are `r na.length` rows with NA datapoints in the value column, from former data cleaning.  
Sites with NA values are `r na.namestring`.  
Majority are within C2B_R3_lsurf (2021), the others have one or two points each due to extreme temperature anomalies.  
2022-06-16: D2B_R3_lsurf_i90_2021, which came from a compromised sensor, is still present. Length = `r D2B_R3_l_length`.  

```{r }

data.cut1 <- data
#view(data.cut1)

```

#### Notes on Site C5A  
See C5A_2021_data_checks.Rmd for plot comparison and decision-making rationale.

C5A R1 lsurf i15 2021 was placed in woodpile.  
C5A R1 m0surf i16 2021 was placed in woodpile.  
C5A R1 m10 i17 2021 seems to have been removed around 3/17/2021.  
R1 m30 and m50 2021 are intact.  
R3 m01surf i24 2021 was placed in woodpile at unknown date.  
  
Degree-day analysis will be performed with ALL C5A sensors except m10 R1, and then with any potentially compromised sensors removed.

R1 m30 and m50 will remain in the set because the data is obviously still valid.

```{r C5A}

#Remove compromised C5A sensors:

data.cut1 <- data.cut1[!(data.cut1$name == "C5A_R1_m10_i17_2021" | data.cut1$name == "C5A_R1_lsurf_i15_2021" | data.cut1$name == "C5A_R1_m0surf_i16_2021" | data.cut1$name == "C5A_R3_m01surf_i24_2021"),]

str(data.cut1)

#Are they all gone?
A <- data.cut1[data.cut1$name == "C5A_R1_m10_i17_2021",] #selects all rows for sensor 17, season 2021
B <- data.cut1[data.cut1$name == "C5A_R1_lsurf_i15_2021",] #selects all rows for sensor 15, season 2021
C <- data.cut1[data.cut1$name == "C5A_R1_m0surf_i16_2021",] #all rows for sensor 16, season 2021
D <- data.cut1[data.cut1$name == "C5A_R3_m01surf_i24_2021",] #all rows for sensor 24, season 2021
str(A)
str(B)
str(C)
str(D)

#There should be only ZEROES.

```






```{r D2B}

data.cut2 <- data.cut1[!(data.cut1$name == "D2B_R3_lsurf_i90_2021"),]

E <- data.cut2[(data.cut2$name == "D2B_R3_lsurf_i90_2021"),]
str(E)

```


```{r three}
#write.csv(as.data.frame(data.cut1), "ALL_A.csv")


```


